Understanding the Socio-Economic Determinants of Voter Behavior: An Analysis of the 2020 U.S. Presidential Election

### 2024-03-16 paper/us_election_2020.qmd
edit based on peer review

```{r}
#| include: false
# Extract posterior samples
# posterior_samples <- as.matrix(political_preferences)
# 
# # Calculate credible intervals (e.g., 95%)
# credible_intervals <- apply(posterior_samples, 2, function(x) quantile(x, c(0.025, 0.975)))
# 
# # Extract coefficient names
# coefficient_names <- colnames(posterior_samples)
# 
# # Create a data frame with coefficient names, coefficient estimates, and credible intervals
# table_data <- data.frame(
#   Posterior_Mean = colMeans(posterior_samples),
#   Credible_Interval_Lower = credible_intervals[1, ],
#   Credible_Interval_Upper = credible_intervals[2, ]
# )
# 
# # Print the table
# print(table_data)

```

@@

## Credibility Interval {#sec-credibility-interval}
90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.

>>>>

@@

## Credibility Interval {#sec-credibility-interval}
90% Credibility intervals graph are shown in @fig-modelresults1 and @fig-modelresults2.
@fig-modelresults1 shows range of coefficient estimates of our model within the 90% probability. Due to the fact that the credibility interval for race "Other" is particularly large, we cannot observe the trend of the 90% credibility intervals of other variables. Therefore we created figure @fig-modelresults2 with the x axis limited from -10 to 10.

Combing @fig-modelresults1 and @fig-modelresults2, we observe statistical significance for the coefficient estimates for students, the Northeast region, individuals identifying with two or more races, individuals identifying with "Other" racial category, Native Americans, Black individuals, and the intercept, Asians in the Midwest region who are employed full-time. The estimates are significant if the intervals do not cross 0. The value for the estimates are in log-odds, indicating that if the coefficient is positive, the individual supports Biden, if negative, the individual supports Trump.
